Learning to Dispatch: A Reinforcement Learning Framework for Train Dispatch Networks

### 2025-04-24 paper/main.tex
Add abstract

\begin{abstract}

\end{abstract}

>>>>

\begin{abstract}
    Train dispatching is a complex and critical task in Operations Research that has traditionally depended on human expertise or static rule-based systems, both of which can lead to inefficiencies and errors. 
    The Train Dispatching Problem (TDP) focuses on optimizing train movements to reduce delays while obeying safety and physical scheduling constraints.
    Reinforcement Learning (RL), particularly Deep Reinforcement Learning (DRL) combined with Graph Neural Networks (GNNs), offers a promising new approach for tackling this challenge in real time. 
    This paper presents a framework that models rail networks as graph structures, using GNNs to process these configurations within an RL framework. 
    This approach integrates Train Operation Graphs, which model individual train activities, with Resource Conflict Graphs to construct a comprehensive problem graph representation. 
    A graph-based Deep Q-Network (DQN) agent is used to evaluate the formulation and shows potential for improving dispatching efficiency by learning effective policies. 
    Expanding on this thesis, further work is needed to refine the action space, address deadlocks, and explore hybrid methods with Mixed-Integer Programming (MIP) solvers. 
    This study lays the groundwork for transforming the train dispatching problem into a reinforcement learning model for further advancements in RL applications to the TDP.
\end{abstract}
